### 2021-07-11 docs/manuscript/manuscript.tex
update manuscript
fix quotation marks

The cladogram of spatiotemporal expression profiles shows that the search space
algorithm selected similar expression mechanisms that very
different topologies can produce.

@@

\section*{Acknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
services used in this work were provided by the VSC (Flemish Supercomputer
Center), funded by Ghent University, FWO and the Flemish Government–department EWI.
All authors acknowledge partial support from CoDI-Universidad de Antioquia under
project "Estudio de la Evolución de Circuitos de Regulación del Desarollo Embrionario a través de
la Biología Evolutiva de Sistemas" code 2017-14367. All authors acknowledge the Colombian
youth for their defense of a better country.

>>>>

@@

\section*{Acknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
services used in this work were provided by the VSC (Flemish Supercomputer
Center), funded by Ghent University, FWO and the Flemish Government–department EWI.
All authors acknowledge partial support from CoDI-Universidad de Antioquia under
project ``Estudio de la Evolución de Circuitos de Regulación del Desarollo Embrionario a través de
la Biología Evolutiva de Sistemas'' code 2017-14367. All authors acknowledge the Colombian
youth for their defense of a better country.
